\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, portrait, margin=1in]{geometry}

\title{\vspace{-2cm}Gyoshil 3-month Plan}
\author{Maria Hwang and Mark Santolucito}
\date{February 2016}

\usepackage{natbib}
\usepackage{graphicx}

\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\setlist[itemize]{noitemsep, topsep=0pt,label={--}}

\begin{document}

\maketitle


\begin{description}
    \item[April 7 - Wk 3] \hfill \\
    \underline{Goal} : Release Monster Appetite as a complete mobile app. \\
    \underline{Approach} : Convert current Meteor implementation (browser-based) to native app using PhoneGap. \\
    \underline{Challenges} :
    \begin{itemize}
        \item Better separation of server and client side logic and resource location.
        \item Learn app ecosystems.
    \end{itemize}


    \item[May 12 - Wk 8] \hfill \\
    \underline{Goal} : Have a template and engine, \textit{GyoshilBuild}, that can synthesize Monster Appetite.\\
    \underline{Approach} : Abstract core components of Monster Appetite and build interface to change said components.\\
    \underline{Challenges} :
    \begin{itemize}
        \item Identify which core components should be abstracted.
        \item Building interface is a large engineering task.
        \item Handling computational abstractions (rather than content like picture or text) requires Programming By Example.
    \end{itemize}

    \item[June 2 -  Wk 11] \hfill \\
    \underline{Goal} : Expand template to synthesize another educational tool, ToolX.\\
    \underline{Approach} : Design and build a second educational tool using \textit{GyoshilBuild}.\\
    \underline{Challenges} :
    \begin{itemize}
        \item Design a tool that is as different from Monster Appetite as \textit{GyoshilBuild} allows.
    \end{itemize}

    \item[June 9 - Wk 12] \hfill \\
    \underline{Goal} : Have user test data with some basic analysis.\\
    \underline{Approach} : Recruit teachers from Geumgang University (Korea), Abraham Joshua Heschel School (NYC, US), and Trinity School (NYC, US). Collect data such as (time to create a tool for a new user) and (return login rate after tutorial session to gauge engagement).\\
    \underline{Challenges} :
    \begin{itemize}
        \item Build data collection/analysis tools into \textit{GyoshilBuild}.
        \item Running a live user study.
    \end{itemize}

    \item[June 16 - End of Wk 13] \hfill \\
    \underline{Goal} : On stage demo of creating two different tools (Monster Appetite and ToolX) with the same template to demonstrate expressiveness of synthesis and ease of use. Present user data results and plan for stage 2 of development - \textit{GyoshilPlatform}.\\
    \underline{Approach} : Don't sleep.\\
    \underline{Challenges} :
    \begin{itemize}
        \item Complete all previous milestones on time.
    \end{itemize}

\end{description}

\end{document}
